Sexual selection improves population fitness: a meta-analysis

### 2018-09-14 meta_analysis_sexual_selection_pop_fitness.Rmd
REML estimates for outcomes table

**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot). Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0. Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative.

@@

#Name columns
colnames(brms.predictions) <- c("Fitness Component", "Estimate", "Error", "LCI", "UCI")

@@

fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```

@@

Taxon.metaanlysis <- predictions.complete %>% 
    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
         Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=2, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-1, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 4.5)))+

@@

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
#Generate predictions without taxon utilising the previously described function

get.predictions.complete2 <- function(newdata){
  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

@@

#Plot the posterior values from the Bayesian model as density ridges
pd <- position_dodgev(height = 0.3)
posterior.plot <- post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+

@@

var.plot.posterior <- post.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  ylab("Environment\n")+
  xlab("\nPhenotypic Variance (lnCVR)")+
  scale_x_continuous(limits = c(-2.1, 1.2), breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1))+
  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+

>>>>

**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values. Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0. Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative. The right side of the table provides the REML estimates with SE and CIs.

@@

#Name columns
colnames(brms.predictions) <- c("Fitness Component", "Bayes Pred.", "Bayes SE", "Bayes LCI", "Bayes UCI")

@@

#Now for REML
model.fitness.components.REML <- rma.mv(g, var.g, mods = ~ 1 + Outcome,
                         random = list(~ 1 | Study.ID,
                                       ~ 1 | Taxon),
                         method = "REML",
                         data = prelim.data)

get.predictions.outcomes <- function(newdata){
  `Body Condition`<-0; `Body Size`<-0; `Development Rate`<-0; `Early Fecundity`<-0; `Ejaculate Quality and Production`<-0; `Extinction Rate`<-0; `Fitness Senescence`<-0; Immunity<-0; Lifespan<-0; `Male Attractiveness`<-0; `Mating Duration`<-0; `Mating Frequency`<-0; `Mating Latency`<-0; `Mating Success`<-0; `Mutant Frequency`<-0; `Offspring Viability`<-0; `Pesticide Resistance`<-0; `Reproductive Success`<-0; Strength<-0
  if(newdata[1] == 'Body Size') `Body Size`<-1
  if(newdata[1] == 'Development Rate') `Development Rate`<-1
  if(newdata[1] == 'Early Fecundity') `Early Fecundity`<-1
  if(newdata[1] == 'Immunity')Immunity<-1
  if(newdata[1] == 'Mating Duration')`Mating Duration`<-1
  if(newdata[1] == 'Pesticide Resistance')`Pesticide Resistance`<-1
  if(newdata[1] == 'Mutant Frequency')`Mutant Frequency`<-1
  if(newdata[1] == 'Body Condition')`Body Condition`<-1
  if(newdata[1] == 'Fitness Senescence')`Fitness Senescence`<-1
  if(newdata[1] == 'Lifespan')Lifespan<-1
  if(newdata[1] == 'Male Attractiveness')`Male Attractiveness`<-1
  if(newdata[1] == 'Mating Frequency')`Mating Frequency`<-1
  if(newdata[1] == 'Mating Latency')`Mating Latency`<-1
  if(newdata[1] == 'Mating Success')`Mating Success`<-1
  if(newdata[1] == 'Strength')Strength<-1
  if(newdata[1] == 'Ejaculate Quality and Production')`Ejaculate Quality and Production`<-1
  if(newdata[1] == 'Extinction Rate')`Extinction Rate`<-1
  if(newdata[1] == 'Offspring Viability')`Offspring Viability`<-1
  if(newdata[1] == 'Reproductive Success')`Reproductive Success`<-1

  predict(model.fitness.components.REML, newmods=c(`Body Condition`, `Body Size`, `Development Rate`, `Early Fecundity`, `Ejaculate Quality and Production`, `Extinction Rate`, `Fitness Senescence`, Immunity, Lifespan, `Male Attractiveness`, `Mating Duration`, `Mating Frequency`, `Mating Latency`, `Mating Success`, `Mutant Frequency`, `Offspring Viability`, `Pesticide Resistance`, `Reproductive Success`, Strength))
}
# Get the predictions for each combination of moderators
predictions.outcomes <- as.data.frame(expand.grid(Outcome = outcome.list.factor))
predictions.outcomes <- cbind(predictions.outcomes, do.call("rbind", apply(predictions.outcomes, 1, get.predictions.outcomes))) %>%
  select(Outcome, pred, se, ci.lb, ci.ub) 
for(i in 2:5) predictions.complete[,i] <- unlist(predictions.complete[,i])

colnames(predictions.outcomes) <- c("Fitness Component", "REML Prediction", "REML SE", "REML LCI", "REML UCI")
predictions.outcomes <- format(predictions.outcomes, digits = 2)

fitness.component.predictions <- fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% `row.names<-`(NULL) %>% format(digits = 2)

left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)

```

```{r}

```

@@

Taxon.metaanlysis <- predictions.complete %>% 
    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
         Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=2, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-1, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 4.5)))+

@@

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
#Generate predictions without taxon utilising the previously described function
get.predictions.complete2 <- function(newdata){
  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

@@

#Plot the posterior values from the Bayesian model as density ridges
pd <- position_dodgev(height = 0.3)
posterior.plot <- post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment")+
  xlab("\nEffect Size (Hedges' g)")+
  # scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  # scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+

@@

var.plot.posterior <- post.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  ylab("Environment\n")+
  xlab("\nPhenotypic Variance (lnCVR)")+
  scale_x_continuous(limits = c(-2.1, 1.2), breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1))+
  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
